---
name: Christopher
surname: Burch
position: "Data Scientist and Consultant"
phone: +1 919 593 2796
email: "christopher.m.burch@gmail.com"
github: burch-cm
linkedin: christophermburch
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "414141"
keep-tex: true
keep-md: true
output:
  vitae::awesomecv:
    keep_md: true
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)

source(here::here("tools.R"))
```

# Summary  
Experienced data scientist, business analyst, and team leader with more than ten 
years of experience in complex systems modeling, analysis, and simulation. I take
pride in transforming data into business insight and building teams that perform 
as more than the sum of their parts.  

# Experience  

```{r experience}

company <- tribble(
  ~ Dates, ~ Position, ~ Company,

  "Sep 2022 - Jul 2025", "Lead Data Scientist", "The MITRE Corporation",
  "Aug 2018 - Sep 2022", "Data Scientist and Senior Consultant", "Grant Leading Technology",
  "Jan 2014 - Jul 2018", "Cofounder / Chief Data Officer", "Cogentis Therapeutics",
  "Jun 2009 - Nov 2011", "Advanced Skills Instructor", "US Army 20th Special Forces Group",
  "Jun 2004 - Jun 2009", "Special Forces Communications NCO", "US Army 10th Special Forces Group"
)

details <- tribble(
  ~ Company, ~ Info,
  "The MITRE Corporation", "Provided technical leadership and guidance in the development
  of advanced data analytics solutions, machine learning models, and artificial intelligence applications.", 
  
  "The MITRE Corporation", "Built systems dynamics and agent-based models to analyze complex 
  systems across multiple domains. Utilized advanced machine learning techniques to model physical, 
  sociological, and epidemiological systems. Developed and validated statistical and causal models 
  to make predictions, explain drivers, and design interventions.",
  
  "The MITRE Corporation", "Presented the findings, recommendations, and the results 
  of complex analysis to a variety of internal and external audiences, including 
  executive-level decision makers.",
  
  "The MITRE Corporation", "Co-Principal Investigator (PI) for an internal research and development 
  project focused on improving outcomes and efficiency in the US Veterans' Affairs 
  disability awards process. Designed research, budgeted, and staffed the team. 
  Conducted technical analysis and changed strategy when necessary based on project needs.",
  
  "The MITRE Corporation", "Assisted with research design and coded a 
  comprehensive meta-analysis of Alzheimer's Disease and related dementias (ADRD), 
  projecting expected ADRD burden at the US State and County level.",
  
  "The MITRE Corporation", "Developed models and simulated encounters to help shipping 
  vessels avoid striking whales in major US shipping lanes.",
  
  "The MITRE Corporation", "Developed company-internal R visualization and data 
  processing packages used by multiple projects across the organization.", 
  
  "The MITRE Corporation", "Build, programmed, and analyzed results of an agent-based
  epidemiological simulation, which led to actionable interventions to prevent the 
  spread of hoof and mouth disease.", 
  
  "The MITRE Corporation", "Trained data analysts and mentored junior data scientists 
  in statistical techniques, complex systems modeling, simulation methods, 
  and data analysis best practices.",
  
  "The MITRE Corporation", "Served as the baseline epidemiology modeling expert 
  for the DARPA Automated Scientific Knowledge Extraction and Modeling (ASKEM) 
  evaluation team from 2023 to 2025.", 
  
  "The MITRE Corporation", "Developed survey instruments and analyzed results 
  for multiple targeted interventions into hiring, promotion, and accommodation 
  decisions across multiple US Federal departments.",
  
  "Grant Leading Technology", "Technical lead for FAA property data visualization, 
  covering more than $9 billion in managed property.",
  
  "Grant Leading Technology", "Built machine learning models to analyze and predict 
  vehicle fleet fuel use, mileage, and accident rates, resulting in improved 
  FAA vehicle training policy.",
  
  "Grant Leading Technology", "Wrote and maintained open-source R packages to interface
  with existing Federal APIs, improving FAA reporting automation and reducing errors.",
  
  "Grant Leading Technology", "Led and managed development of the FAA-wide vehicle recall 
  status tracking system, reducing outstanding vehicle recalls by 90%.",
  
  "Grant Leading Technology", "Applied systems theory to model complex interactions 
  between business units, and proposed workflow process improvements based on those
  models.",
  
  "Grant Leading Technology", "Wrote, built, and administered rollout of a new 
  company-wide employee evaluation system.",
  
  "Cogentis Therapeutics", "Conducted statistical power analysis of proposed experimental 
  pathways, leading to reduced experimental risk and improved statisitcal lift.", 
  
  "Cogentis Therapeutics", "Developed financial models which reduced 
  investor risk and experimental cost while maintaining research objectives.",
  
  "Cogentis Therapeutics", "Created company data standard operating procedures (SOP), 
  code books, and data dictionaries.",
  
  "Cogentis Therapeutics", "Prepared data visualizations for company communication, 
  publication, and grant writing.",
  
  "US Army 20th Special Forces Group", "Senior CQB/Close Combat Instructor for US
  Army, US Navy, and NATO forces in close quarters combat (CQB), fighting in 
  built-up areas (FIBU), advanced urban combat (SFAUC), and advanced special 
  operations (ASO).",
  
  "US Army 20th Special Forces Group", "Lead a team of 5 – 10 junior instructors; 
  responsible for subordinate instruction in firearms and small unit tactics 
  proficiency, range preparation, and field exercise coordination.",
  
  "US Army 20th Special Forces Group", "Developed a metrics-based training evaluation 
  system to A/B test multiple techniques.",
  
  "US Army 10th Special Forces Group", "Trained and advised more than 2,000 foreign 
  military and police force personnel in patrolling, advanced urban combat, 
  marksmanship, and mission planning.",
  
  "US Army 10th Special Forces Group", "Participated in more than 250 named missions 
  across Afghanistan, Africa, and Eastern Europe in support of US and NATO 
  counter-terrorism efforts."
)


company %>%
  left_join(details, by = "Company") %>%
  detailed_entries(Position, Dates, Company, why = Info)
```


# Technical Skills  
```{r technical-skills}
tribble(
    ~ With, ~ What,
    "Areas of Expertise", "Complex Systems Modeling and Simulation, Research Design, Statistical Analysis, Machine Learning",
    "Languages", "R, Python, Julia, SQL, M, VBA",
    "Software", "Excel, Tableau, Git, Linux, Windows, Shiny, Apache Spark",
    "Techniques", "Bayesian methods, Agile Software Development, Causal inference"
) |> 
    detailed_entries(what = What, with = With)
```


# Education  

```{r education}

tribble(
  ~ Year, ~ Degree, ~ Institution, ~ Details,
  "2015-2017", "MicroMasters Certificate",
  "Massachussetts Institute of Technology", "Graduate training in Data, Economics, and 
  Developmental Policy (DEDP)",
  "2013-2015", "Master of Business Administration", "Johns Hopkins University",
  "Double Specialization in Enterprise Risk Management (ERM) and Marketing",
  "2011-2013", "Bachelor of Arts, Organizational Management", "Arizona State University", "SALUTE National Honors Society"
) %>% 
  detailed_entries(Degree, Year, Institution, why = Details)
```
\newpage

# Current Certifications  

```{r certs}
tribble(
    ~ Name, ~ Org,
    "Data Science Specialization", "Johns Hopkins University",
    "IBM Machine Learning Specialization", "IBM",
    "Lean Six Sigma Yellow Belt", "Grant Leading Technology",
    "Certified Risk Analyst (CRA)", "Global Academy of Finance and Management"
) %>%
  detailed_entries(with = Name, what = Org)
```

# Memberships  

```{r membership}
tribble(
    ~ Name, ~ Role,
    "ASTM International", "Voting Member on Subcommittees for Sampling/Statistics, Data Management, Fleet Management",    
    "Data Science Council of America", "Member at Large"
) %>%
  detailed_entries(with = Name, what = Role)
```

# Awards

```{r awards}
tribble(
  ~Year, ~Award, ~Org, ~Desc,
  "2023 & 2024", "SPARK Award", "The MITRE Corporation", "MITRE-internal award recongnizing significant contributions and innovation in research.",
  "2020 & 2016", "Finalist", "MassChallenge", "Startup incubator and business model contest. Selected as a Top 20 Finalist, the incubator's highest honor, from more than 500 startups from across the globe.",
  "2015", "1st Place", "Neuro StartUp Challenge", "NIH / Oxbridge - funded competition to develop existing NIH patents.",
  "2015", "1st Place", "Wake Forest Business School Business Case Competition", "Biotech business case competition with Boston Scientific.",
  "2014", "Director's Award for Excellence", "Federal Bureau of Investigation", "First unit outside of the FBI to receive this award.",
  "2009", "Bronze Star Medal", "US Army" , "Awarded for combat actions in support of Operation Enduring Freedom (OEF)") %>%
  detailed_entries(Award, Year, Org, why = Desc)
```

# Publications

```{r}
bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

