---
name: Christopher
surname: Burch
position: "Data Scientist and Consultant"
address: "Fredericksburg, Virginia"
phone: +1 919 593 2796
www: cmburch.com
email: "christopher.m.burch@gmail.com"
github: burch-cm
linkedin: christophermburch
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "414141"
keep-md: true
output:
  vitae::awesomecv:
    keep_tex: true  

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)

source(here::here("tools.R"))
```

# Summary  
Experienced data scientist, business analyst, and team leader with ten years of 
experience in complex systems modeling, analysis, and simulation. I take pride in
transforming data into business insight and building teams that perform as more 
than the sum of their parts.  

# Experience  

```{r experience}

company <- tribble(
  ~ Dates, ~ Position, ~ Company,
  "2022 - 2025", "Lead Data Scientist", "The MITRE Corporation",
  "2018 - 2022", "Data Scientist and Consultant", "Grant Leading Technology",
  "2014 - 2018", "Cofounder / Chief Data Officer", "Cogentis Therapeutics",
  "2009 - 2011", "Advanced Skills Instructor", "US Army 20th Special Forces Group",
  "2004 - 2009", "Special Forces Communications NCO", "US Army 10th Special Forces Group"
)

details <- tribble(
  ~ Company, ~ Info,
  "The MITRE Corporation", "Developed and validated statistical models to design 
  interventions into social, logistical, and physical engineering problems, 
  with a focus on the modeling and analysis of complex systems.",
  
  "The MITRE Corporation", "Designed, budgeted, staffed, and served as 
  Co-Principal Investigator (PI) for a multi-year research project focused on improving 
  outcomes and efficiency in the US Veterans' Affairs disability awards process.",
  
  "The MITRE Corporation", "Developed models and simulated encouters to help shipping 
  vessels avoid striking whales in major US shipping lanes.",
  
  "The MITRE Corporation", "Presented the findings, recommendations, and the results 
  of complex analysis to a variety of internal and external audiences, including 
  executive-level decison makers.",
  
  "The MITRE Corporation", "Developed company-internal R visualization and data 
  processing packages used by multiple projects across the organization.", 
  
  "The MITRE Corporation", "Build, programmed, and analyzed results of an agent-based
  epidemiologocal simulation, which led to actionable interventions to prevent the 
  spread of disease in commercial agricultural populations.", 
  
  "The MITRE Corporation", "Trained data analysts and mentored junior data scientists 
  in statatiscal techniques, complex systems modeling, simulation methods, 
  and data analysis best practices.",
  
  "The MITRE Corporation", "Assisted with reserach design and coded the a 
  comprehensive metaanalysis of Alzheimer's Disease and related dementias (ADRD), 
  projecting expected ADRD burden at the US State and County level.",
  
  "The MITRE Corporation", "Lead a baseline testing team and served as the 
  epidemiology modeling expert for the DARPA Automated Scientific Knowledge 
  Extraction and Modeling (ASKEM) evaluation over three years.", 
  
  "The MITRE Corporation", "Developed survey response questions and analyzed results 
  for multiple trageted inteventions into hiring, promotion, and accommodation 
  decisions across multiple US Federal departments.",
  
  
  "Grant Leading Technology", "Technical lead for FAA property data visualization, 
  covering more than $9 billion in managed property.",
  "Grant Leading Technology", "Built machine learning models to analyze and predict 
  vehicle fleet fuel use, mileage, and accident rates, resulting in improved 
  FAA vehicle training policy.",
  "Grant Leading Technology", "Wrote and maintained open-source R packages to interface
  with existing Federal APIs, improving FAA reporting automation and reducing errors.", 
  "Grant Leading Technology", "Managed development of the FAA-wide vehicle recall 
  status tracking system, reducing outstanding vehicle recalls by 90%.",
  "Grant Leading Technology", "Applied systems theory to model complex interactions 
  between business units, and proposed workflow process improvements based on those
  models.",
  "Grant Leading Technology", "Wrote, built, and administered rollout of a new 
  company-wide employee evaluation system.",
  "Cogentis Therapeutics", "Developed financial models which reduced 
  investor risk and controlled experimental risk for increased stability in the 
  startup ecosystem.",
  "Cogentis Therapeutics", "Created company data standard operating procedures (SOP), 
  code books, and data dictionaries.",
  "Cogentis Therapeutics", "Prepared data visualizations for company communication, 
  publication, and grantwriting.",
  "US Army 20th Special Forces Group", "Senior CQB/Close Combat Instructor for US
  Army, US Navy, and NATO forces in close quarters combat (CQB), fighting in 
  built-up areas (FIBU), advanced urban combat (SFAUC), and advanced special 
  operations (ASO).",
  "US Army 20th Special Forces Group", "Lead a team of 5 – 10 junior instructors; 
  responsible for subordinate instruction in firearms and small unit tactics 
  proficiency, range preparation, and field exercise coordination.",
  "US Army 20th Special Forces Group", "Developed a metrics-based training evaluation 
  system to A/B test multiple techniques.",
  "US Army 10th Special Forces Group", "Trained and advised more than 2,000 foreign 
  military and police force personnel in patrolling, advanced urban combat, 
  marksmanship, and mission planning.",
  "US Army 10th Special Forces Group", "Participated in more than 250 named missions 
  across Afghanistan, Africa, and Eastern Europe in support of US and NATO 
    counterterrism efforts."
)

company %>%
  left_join(details, by = "Company") %>%
  detailed_entries(Position, Dates, Company, why = Info)
```

# Technical Skills  
```{r technical-skills}
tribble(
    
)
```


# Education  

```{r education}

tribble(
  ~ Year, ~ Degree, ~ Institution, ~ Details,
  "2015-2017", "MicroMasters Certificate",
  "Massachussetts Institute of Technology", "Graduate training in Data, Economics, and 
  Developmental Policy (DEDP)",
  "2013-2015", "Master of Business Administration", "Johns Hopkins University",
  "Double Specialization in Enterprise Risk Management (ERM) and Marketing",
  "2011-2013", "Bachelor of Arts, Organizational Management", "Arizona State University Global Campus", "SALUTE National Honors Society"
) %>% 
  detailed_entries(Degree, Year, Institution, why = Details)
```
\newpage

# Current Certifications  

```{r certs}
tribble(
    ~ Name, ~ Org,
    "Certified Professional Property Specialist (CPPS)", 
    "National Property Management Association",
    "Lean Six Sigma Yellow Belt", "Grant Leading Technology",
    "Certified Risk Analyst (CRA)", "Global Academy of Finance and Management"
) %>%
  detailed_entries(with = Name, what = Org)
```

# Memberships  

```{r membership}
tribble(
    ~ Name, ~ Role,
    "ASTM International", "Voting Member on Subcommittees for Sampling/Statistics, Data Management, Fleet Management",    
    "National Property Management Association", "Member, Federal Chapter",
    "Data Science Council of America", "Member at Large"
) %>%
  detailed_entries(with = Name, what = Role)
```

# Awards

```{r awards}
tribble(
  ~Year, ~Award, ~Org, ~Desc,
  "2023", "SPARK Award", "The MITRE Corporation", "",
  
  "2020 & 2016", "Finalist", "MassChallenge", "Startup incubator and business model contest. Selected as a Top 20 Finalist, the incubator's highest honor, from more than 500 startups from across the globe.",
  "2015", "1st Place", "Neuro StartUp Challenge", "NIH / Oxbridge - funded competition to develop existing NIH patents.",
  "2015", "1st Place", "Wake Forest Business School Business Case Competition", "Biotech business case competition with Boston Scientific.",
  "2014", "Director's Award for Excellence", "Federal Bureau of Investigation", "First unit outside of the FBI to recieve this award.",
  "2009", "Bronze Star Medal", "US Army" , "Awarded for combat actions in Logar, Afghanistan.") %>%
  detailed_entries(Award, Year, Org, why = Desc)
```

# Publications

```{r}
bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

