%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Christopher}{Burch}

\position{Data Scientist and Consultant}
\address{Fredericksburg, Virginia}

\mobile{+1 919 593 2796}
\email{\href{mailto:christopher.m.burch@gmail.com}{\nolinkurl{christopher.m.burch@gmail.com}}}
\homepage{cmburch.com}
\github{burch-cm}
\linkedin{christophermburch}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {December 2020}
    {Christopher Burch~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{summary}{%
\section{Summary}\label{summary}}

An experienced data analyst and team leader. I take pride in
transforming data into business insight and building teams that perform
as more than the sum of their parts.

\hypertarget{experience}{%
\section{Experience}\label{experience}}

\begin{cventries}
    \cventry{Data Scientist and Consultant}{Grant Leading Technology}{}{2018 - Present}{\begin{cvitems}
\item Technical lead for FAA property data visualization, 
  covering more than \$9 billion in managed property.
\item Built machine learning models to analyze and predict 
  vehicle fleet fuel use, mileage, and accident rates, resulting in improved 
  FAA vehicle training policy.
\item Wrote and maintained open-source R packages to interface
  with existing Federal APIs, improving FAA reporting automation and reducing errors.
\item Managed development of the FAA-wide vehicle recall 
  status tracking system, reducing outstanding vehicle recalls by 90\%.
\item Applied systems theory to model complex interactions 
  between business units, and proposed workflow process improvements based on those
  models.
\item Wrote, built, and administered rollout of a new 
  company-wide employee evaluation system.
\end{cvitems}}
    \cventry{Cofounder / Chief Data Officer}{Cogentis Therapeutics}{}{2014 - 2018}{\begin{cvitems}
\item Developed financial models which reduced 
  investor risk and controlled experimental risk for increased stability in the 
  startup ecosystem.
\item Created company data standard operating procedures (SOP), 
  code books, and data dictionaries.
\item Prepared data visualizations for company communication, 
  publication, and grantwriting.
\end{cvitems}}
    \cventry{Advanced Skills Instructor}{US Army 20th Special Forces Group}{}{2009 - 2011}{\begin{cvitems}
\item Senior CQB/Close Combat Instructor for US
  Army, US Navy, and NATO forces in close quarters combat (CQB), fighting in 
  built-up areas (FIBU), advanced urban combat (SFAUC), and advanced special 
  operations (ASO).
\item Lead a team of 5 – 10 junior instructors; 
  responsible for subordinate instruction in firearms and small unit tactics 
  proficiency, range preparation, and field exercise coordination.
\item Developed a metrics-based training evaluation 
  system to A/B test multiple techniques.
\end{cvitems}}
    \cventry{Special Forces Communications NCO}{US Army 10th Special Forces Group}{}{2004 - 2009}{\begin{cvitems}
\item Trained and advised more than 2,000 foreign 
  military and police force personnel in patrolling, advanced urban combat, 
  marksmanship, and mission planning.
\item Participated in more than 250 named missions 
  across Afghanistan, Africa, and Eastern Europe in support of US and NATO 
    counterterrism efforts.
\end{cvitems}}
\end{cventries}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{MicroMasters Certificate}{Massachussetts Institute of Technology}{}{2015-2017}{\begin{cvitems}
\item Graduate training in Data, Economics, and 
  Developmental Policy (DEDP)
\end{cvitems}}
    \cventry{Master of Business Administration}{Johns Hopkins University}{}{2013-2015}{\begin{cvitems}
\item Double Specialization in Risk Management and Marketing
\end{cvitems}}
    \cventry{Bachelor of Arts, Organizational Management}{Arizona State University Global Campus}{}{2011-2013}{\begin{cvitems}
\item SALUTE National Honors Society
\end{cvitems}}
\end{cventries}
\newpage

\hypertarget{current-certifications}{%
\section{Current Certifications}\label{current-certifications}}

\begin{cventries}
    \cventry{National Property Management Association}{Certified Professional Property Specialist (CPPS)}{}{}{\vspace{-4mm}}
    \cventry{Grant Leading Technology}{Lean Six Sigma Yellow Belt}{}{}{\vspace{-4mm}}
    \cventry{Global Academy of Finance and Management}{Certified Risk Analyst (CRA)}{}{}{\vspace{-4mm}}
\end{cventries}

\hypertarget{awards}{%
\section{Awards}\label{awards}}

\begin{cventries}
    \cventry{Finalist}{MassChallenge}{}{2020 \& 2016}{\begin{cvitems}
\item Startup incubator and business model contest. Selected as a Top 20 Finalist, the incubator's highest honor, from more than 500 startups from across the globe.
\end{cvitems}}
    \cventry{1st Place}{Neuro StartUp Challenge}{}{2015}{\begin{cvitems}
\item NIH / Oxbridge - funded competition to develop existing NIH patents.
\end{cvitems}}
    \cventry{1st Place}{Wake Forest Business School Business Case Competition}{}{2015}{\begin{cvitems}
\item Biotech business case competition with Boston Scientific.
\end{cvitems}}
    \cventry{Director's Award for Excellence}{Federal Bureau of Investigation}{}{2014}{\begin{cvitems}
\item First unit outside of the FBI to recieve this award.
\end{cvitems}}
    \cventry{Bronze Star Medal}{US Army}{}{2009}{\begin{cvitems}
\item Awarded for combat actions in Logar, Afghanistan.
\end{cvitems}}
\end{cventries}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{bibliography}{}
\leavevmode\hypertarget{ref-R-altfuelr}{}%
1. Burch, C. (2020). \emph{Altfuelr: An interface to the nrel alternate
fuels locator}. \url{https://CRAN.R-project.org/package=altfuelr}

\leavevmode\hypertarget{ref-R-vindecodr}{}%
2. Burch, C. (2020). \emph{Vindecodr: An interface to the us department
of transportation vin decoder}.
\url{https://CRAN.R-project.org/package=vindecodr}

\end{document}
